A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries

### 2022-01-04 src/docs_04-01-22-update/04-01-22-update.Rmd
Finish off presentation for lab group #50

@@

Final model selected:

\begin{align}
    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \theta_{iat}.
\end{align}

@@

>>>>

## Statistical model

Fit 13 models of the form:

\begin{align}
    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \delta_{itk} + \theta_{ita}.
\end{align}

\begin{table}[htb]
\centering
\begin{tabularx}{\textwidth}{llll}
\midrule
Model ID & Spatial structure & Temporal structure & Spatio-temporal interaction \\ 
\midrule
1 & None & None & \xmark \\
2 & IID & None & \xmark \\
3 & Besag & None & \xmark \\
4 & None & IID & \xmark \\
5 & IID & IID & \xmark \\
5x & IID & IID & \cmark \\
6 & Besag & IID & \xmark \\
6x & Besag & IID  & \cmark \\
7 & None & AR1 & \xmark \\
8 & IID & AR1 & \xmark \\
8x & IID & AR1 & \cmark \\
9 & Besag & AR1 & \xmark \\
9x & Besag & AR1 & \cmark \\
\midrule
\end{tabularx}
\end{table}

@@

@@

## Next steps

* Feedback on paper from people who know more about country contexts
* Connect more to policy. For example by replicating Katie's "number of new infections by risk group" spreadsheet
* Add logistic regression model for proportion of non-regular partner(s) who are KP
